Data Exploration: IUCN and AquaMaps

### 2016-07-30 coralmaps/coral_maps.Rmd
first pass analysis - assuming that removing deep cells does not affect AquaMaps (since AM is theoretically filtered to shallows as well)

library(ggplot2)
library(maps)
library(readr)
library(data.table)
library(raster)
library(tidyr)
library(dplyr)
library(stringr)

@@

dir_anx <- file.path(dir_M, 'git-annex/globalprep/SPP_ICO')
dir_fig <- file.path(dir_git, 'figures')
dir_data <- file.path(dir_git, 'data')

@@

###

@@

>>>>

library(ggplot2)
library(maps)
library(readr)
library(raster)
library(rgdal)
library(tidyr)
library(dplyr)
library(stringr)

@@

dir_anx <- file.path(dir_M, 'git-annex/globalprep/spp_ico')
dir_fig <- file.path(dir_git, 'figures')
dir_data <- file.path(dir_git, 'data')

@@

if(!file.exists(file.path(dir_git, 'coralmaps', 'bathy_cells.csv'))) {

  poly_bath <- readOGR(dsn = file.path(path.expand(dir_git), 'coralmaps/ne_10m_bathymetry_K_200'), 
                       layer = 'ne_10m_bathymetry_K_200', 
                       stringsAsFactors = TRUE)

  ### LOICZID cell ID numbers - used in plotting rasters
  loiczid_raster_file  <- file.path(dir_git, 'shiny/data/loiczid_raster.grd')
  loiczid_raster       <- raster(loiczid_raster_file)
  names(loiczid_raster) <- 'loiczid'

  bath_list <- raster::extract(loiczid_raster, poly_bath, 
                             weights = TRUE, normalizeWeights = FALSE,
                             progress = 'text')
  bath_df <- lapply(bath_list, function(x) {as.data.frame(x)}) %>%
    bind_rows() %>%
    rename(loiczid = value) %>%
    group_by(loiczid) %>%
    summarize(weight = sum(weight))

  ### generate raster?
  bath_raster <- subs(loiczid_raster, bath_df, by = 'loiczid', which = 'weight')
  values(bath_raster)[values(bath_raster) > 5] <- NA

  write_csv(bath_df, file.path(dir_git, 'coralmaps', 'bathy_cells.csv'))
  ### probably want to filter to just 100% 200m+
}

@@

``` {r}
### find spp depth limits
### focus just on corals?

if(!file.exists(file.path(dir_git, 'coralmaps', 'coral_spp_depth_raw.csv'))) {

  library(jsonlite)
  api_key <- 'fb71ae836f415f04f41176f6d30c4a9e4cea620d46b9e5021bf2fb142ea51bf5'

  get_from_api <- function(url, param) {
      api_info <- fromJSON(sprintf(url, param, api_key)) %>%
        data.frame(stringsAsFactors = FALSE)
  }

  mc_get_from_api <- function(url, param_vec) {
    numcores = ifelse(Sys.info()[['nodename']] == 'mazu', 12, 1)
    out_df <- parallel::mclapply(param_vec, 
                            function(x) get_from_api(url, x),
                            mc.cores = numcores) %>% 
      bind_rows() 
    out_df <- out_df %>%
      setNames(names(.) %>%
                 str_replace('result.', ''))
  }

  ### get species list
  data_file <- file.path(dir_data, 'spp_list_w_area_trimmed.csv')
  spp_map_pairs <- read.csv(data_file, stringsAsFactors = FALSE) %>%
    filter(!is.na(popn_category)) %>% ### filter out unassessed species
    filter(!is.na(sm_perc))           ### filter out NA maps

  coral_spp_sid <- spp_map_pairs %>%
    filter(str_detect(spp_group, 'CORAL')) %>%
    .$iucn_sid

  spp_narr_url <- 'http://apiv3.iucnredlist.org/api/v3/species/narrative/id/%s?token=%s'
  spp_narr     <- mc_get_from_api(spp_narr_url, coral_spp_sid)

  write_csv(spp_narr, file.path(dir_git, 'coralmaps', 'coral_spp_narratives.csv'))

  spp_depth <- spp_narr %>%
    select(iucn_sid = species_id, habitat)
  write_csv(spp_depth, file.path(dir_git, 'coralmaps', 'coral_spp_depth_raw.csv'))
  ### manually find max depths from this
}

``` {r}

### load iucn spp_cells
coral_files <- list.files(file.path(dir_anx, 'v2016', 'iucn_intersections'), 
                          pattern = 'CORAL*.*',
                          full.names = TRUE)
iucn_coral_cells <- lapply(coral_files, read_csv)
